Mental health issue linked to major crimes

### 2024-09-26 Paper/Paper.qmd
Final Draft of Paper
Adding citation for packages and equations. Enhancing graphs and table of contents.

The data used in this paper came from the Open Data Toronto portal through the library opendatatoronto [@OpenDataToronto]. Data were cleaned and analyzed using the open source statistical programming language R [@R]. Libraries tidyverse [@tidyverse], dplyr [@dplyr], and lubridate [@lubridate] were used for simulating, cleaning and testing. Graphics were made using ggplot2 [@ggplot2], gt[@gt] and broom[@broom].

The cleaned data comes from two raw data sets: Mental Health Act Apprehensions Dataset, which contains records of Mental Health Act (MHA) reports grouped by police division, and Major Crime Indicators Dataset, which includes records of crimes similarly categorized by police division. The cleaned data set aggregates the number of MHA reports and crimes for each district, providing a comprehensive overview of the relationship between mental health reports and crime incidents across the specified districts.

@@

$$
C = 6748.244 + 2.451 \times MHA 
$$

@@

This paper investigated the relationship between the number of Mental Health Act Apprehensions and the major crime indicator, according to Toronto Police Services data retrieved from OpenData Toronto. Results shows that as the number of MHA reports rises, the major crime indicator also increases, based on data from 2014 to 2024. Furthermore, there appears to be a positive linear relationship between the number of MHA reports and the number of major crime indicator, which can be expressed as a linear model $C = 6748.244 + 2.451 \times MHA$.

>>>>

## 2.1 Packages
The data used in this paper came from the Open Data Toronto portal through the library opendatatoronto [@OpenDataToronto]. Data were cleaned and analyzed using the open source statistical programming language R [@R]. Libraries tidyverse [@tidyverse], dplyr [@dplyr], and lubridate [@lubridate] were used for simulating, cleaning and testing. Graphics were made using ggplot2 [@ggplot2], gt[@gt] and broom[@broom].

## 2.2 Clean data process
The cleaned data comes from two raw data sets: Mental Health Act Apprehensions Dataset, which contains records of Mental Health Act (MHA) reports grouped by police division, and Major Crime Indicators Dataset, which includes records of crimes similarly categorized by police division. The cleaned data set aggregates the number of MHA reports and crimes for each district, providing a comprehensive overview of the relationship between mental health reports and crime incidents across the specified districts.

@@

\begin{equation}
C = 6748.244 + 2.451 \times MHA 
\label{eq:linear}
\end{equation}

@@

This paper investigated the relationship between the number of Mental Health Act Apprehensions and the major crime indicator, according to Toronto Police Services data retrieved from OpenData Toronto. Results shows that as the number of MHA reports rises, the major crime indicator also increases, based on data from 2014 to 2024. Furthermore, there appears to be a positive linear relationship between the number of MHA reports and the number of major crime indicator, which can be expressed as a linear model $C = 6748.244 + 2.451 \times MHA$ \eqref{eq:linear}.
